### 2018-04-09 Annotations/Annotations.tex
Updated introduction

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document}
\section{How to Generate a Good Word Embedding?}
Paper by Lai et al.\cite{lai2016generate}
\begin{itemize}
\item{Word embedding, also known as distributed word
representation, can capture both the semantic and syntactic
information of words from a large unlabeled corpus
and has attracted considerable attention from many researchers.
In recent years, several models have been proposed,
and they have yielded state-of-the-art results in many
natural language processing (NLP) tasks.}
\item{We observe that almost
all methods for training word embeddings are based on the
same distributional hypothesis: words that occur in similar
contexts tend to have similar meanings.}
\item{Training on a large corpus
generally improves the quality of word embeddings,
and training on an in-domain corpus can significantly
improve the quality of word embeddings for a specific
task.}
\item{Previous works have shown that models that predict the target word capture the paradigmatic relations between words}
\item{we can conclude that using a larger corpus can yield a better embedding, when the corpora are in the same domain}
\item{In most of the tasks, the influence of the corpus domain is
dominant. In different tasks, it impacts performance in the
different ways}
\item{The corpus
domain is more important than the corpus size. Using an indomain
corpus significantly improves the performance for a
given task, whereas using a corpus in an unsuitable domain
may decrease performance. }
\end{itemize}
\bibliographystyle{unsrt}
\bibliography{Bibliography}
\end{document}

>>>>

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document}
\section{How to Generate a Good Word Embedding?}
Paper by Lai et al.\cite{lai2016generate}
\begin{itemize}
\item{Word embedding, also known as distributed word
representation, can capture both the semantic and syntactic
information of words from a large unlabeled corpus
and has attracted considerable attention from many researchers.
In recent years, several models have been proposed,
and they have yielded state-of-the-art results in many
natural language processing (NLP) tasks.}
\item{We observe that almost
all methods for training word embeddings are based on the
same distributional hypothesis: words that occur in similar
contexts tend to have similar meanings.}
\item{Training on a large corpus
generally improves the quality of word embeddings,
and training on an in-domain corpus can significantly
improve the quality of word embeddings for a specific
task.}
\item{Previous works have shown that models that predict the target word capture the paradigmatic relations between words}
\item{we can conclude that using a larger corpus can yield a better embedding, when the corpora are in the same domain}
\item{In most of the tasks, the influence of the corpus domain is
dominant. In different tasks, it impacts performance in the
different ways}
\item{The corpus
domain is more important than the corpus size. Using an indomain
corpus significantly improves the performance for a
given task, whereas using a corpus in an unsuitable domain
may decrease performance. }
\end{itemize}
\section{Better Word Representations with Recursive Neural Networks for Morphology}
Paper by Luong et al.\cite{luong2013better}
\begin{itemize}
\item{The use of word representations or word clusters
pretrained in an unsupervised fashion from lots of
text has become a key “secret sauce” for the success
of many NLP systems in recent years, across
tasks including named entity recognition, part-ofspeech
tagging, parsing, and semantic role labeling.}
\item{The main advantage of having such a distributed
representation over word classes is that it can capture
various dimensions of both semantic and syntactic
information in a vector where each dimension
corresponds to a latent feature of the word. As
a result, a distributed representation is compact,
less susceptible to data sparsity, and can implicitly
represent an exponential number of word clusters.}
\item{The Rare-word dataset introduced by Luong et al.}
\end{itemize}
\bibliographystyle{unsrt}
\bibliography{Bibliography}
\end{document}

### 2018-04-09 Thesis/Parts/Introduction/Introduction.tex
Updated introduction

\subsection{domain specific}
Earlier work on this topic, concerning academic articles, by Truong[TODO: CITE] states the following: "Our findings clearly evinced that in-domain training of the
word embeddings can drastically improve the process of document clustering. In fact, the
effect is even stronger than the number of training examples and the model architecture.
However, too isolated training can lead to a failure of several clustering algorithms, such
as DBSCAN, due to a too dense vocabulary". This was also found by Lai et al, who state: "The corpus domain is more important than the corpus size. Using an indomain corpus significantly improves the performance for a given task, whereas using a corpus in an unsuitable domain may decrease performance". These statements both indicate that an indomain corpus improves the performance of word-vectors for those specific domains. However, domain specific validation techniques do not exist currently. Multiple generic validation sets have been published [TODO: insert comparison methods]. These sets have been used in multiple studies of word-vectors[TODO REFERENCE] whom corpus existed of simular generic information [TODO: INSERT CORPUS DETAILS]. These validation methods are limited to the non domain specific fields. 
\subsection{Embedding validation}[IS THIS TRUE?]Not published results of the study by Truong show high error rates on the validation scores, while the word-vectors seem to work well on document clustering. This seems to indicate that the word-vectors are well suited, but no objective validation method can confirm or deny this. Therefore, we propose the validation of word-embeddings through [SOLUTION].

>>>>

\subsection{domain specific}
Earlier work on this topic, concerning academic articles, by Truong[TODO: CITE] states the following: "Our findings clearly evinced that in-domain training of the
word embeddings can drastically improve the process of document clustering. In fact, the
effect is even stronger than the number of training examples and the model architecture.
However, too isolated training can lead to a failure of several clustering algorithms, such
as DBSCAN, due to a too dense vocabulary". This was also found by Lai et al, who state: "The corpus domain is more important than the corpus size. Using an in-domain corpus significantly improves the performance for a given task, whereas using a corpus in an unsuitable domain may decrease performance". These statements both indicate that an in-domain corpus improves the performance of word-vectors for those specific domains. However, domain specific validation techniques do not exist currently. Multiple generic validation sets have been published such as:

the Rare-word dataset introduced by Luong et al in their paper "Better Word Representations with Recursive Neural Networks for Morphology"\cite{luong2013better}, 
the MEN test collection\cite{EBruniMENCollection} and the WordSimilarity-353 test collection\cite{EGabrilovichWScollection}.

These sets have been used in multiple studies of word-vectors[TODO REFERENCE] which corpus existed of similar generic information [TODO: INSERT CORPUS DETAILS]. These validation methods are limited to the non domain specific fields. 
\subsection{Embedding validation}Not published results of the study by Truong show high error rates on the validation scores, while the word-vectors seem to work well on document clustering. This seems to indicate that the word-vectors are well suited, but no objective validation method can confirm or deny this. Therefore, we propose the validation of word-embeddings through [SOLUTION].

\begin{tabular}{c c c c}
&WordSim & Men & RareWords\\
Lowest & 0.38 & 0.54 & 0.29 \\
Highest & 0.49 & 0.61 & 0.32\\
Average & 0.45 & 0.59 & 0.32\\
Baseline & 0.64 & 0.68 & 0.34\\
\end{tabular}
